Overconfidence and settlement: evidence from Mexican labor courts\thanks{We would like to thank Sebastian Garcia, Isaac Meza, Diana Roman, and Monica Zamudio (``la banda pesada'' and ``los mas aca'') for superhuman research assistance. All errors are ours.}

### 2017-08-15 Paper/Tables/ITT_ATT.tex
Pendientes "More to do stuff"

% Table generated by Excel2LaTeX from sheet 'ITT_ATT'
\begin{tabular}{lrrlrlrlrrr}
      & \multicolumn{7}{c}{Conciliation}                      & \multicolumn{1}{c}{Calculator Plaintiff} & \multicolumn{1}{c}{Calculator Defendant} & \multicolumn{1}{c}{Calculator Both} \\
\cmidrule{2-11}      & \multicolumn{1}{c}{ITT} & \multicolumn{1}{c}{ITT} & \multicolumn{2}{c}{ATT (Plaintiff)} & \multicolumn{2}{c}{ATT  (Defendant)} & \multicolumn{1}{c}{ATT (Both)} & \multicolumn{3}{c}{First Stage} \\
\cmidrule{2-11}Treatment  & \multicolumn{1}{l}{0.0540*} & \multicolumn{1}{l}{0.0486**} &       &       &       &       &       & \multicolumn{1}{l}{0.722***} & \multicolumn{1}{l}{0.635***} & \multicolumn{1}{l}{0.489***} \\
      & \multicolumn{1}{l}{(0.0264)} & \multicolumn{1}{l}{(0.0202)} &       &       &       &       &       & \multicolumn{1}{l}{(0.0215)} & \multicolumn{1}{l}{(0.0220)} & \multicolumn{1}{l}{(0.0263)} \\
Calculator  & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & 0.0673** &       & 0.0766** &       & 0.0995** &       &       &  \\
(instrumented with ITT) & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & (0.0281) &       & (0.0317) &       & (0.0417) &       &       &  \\
Calculator  &       &       &       & \multicolumn{1}{l}{-0.0141} &       & \multicolumn{1}{l}{-0.0158} &       &       &       &  \\
(instrumented with ITT \& ITT*EP) &       &       &       & \multicolumn{1}{l}{(0.0249)} &       & \multicolumn{1}{l}{(0.0286)} &       &       &       &  \\
Constant  & \multicolumn{1}{l}{0.159***} & \multicolumn{1}{l}{0.124***} & 0.123*** & \multicolumn{1}{l}{0.131***} & 0.125*** & \multicolumn{1}{l}{0.129***} & 0.125*** & \multicolumn{1}{l}{0.0150} & \multicolumn{1}{l}{-0.0150} & \multicolumn{1}{l}{-0.00841} \\
      & \multicolumn{1}{l}{(0.0184)} & \multicolumn{1}{l}{(0.0286)} & (0.0293) & \multicolumn{1}{l}{(0.0269)} & (0.0273) & \multicolumn{1}{l}{(0.0268)} & (0.0280) & \multicolumn{1}{l}{(0.0319)} & \multicolumn{1}{l}{(0.0289)} & \multicolumn{1}{l}{(0.0287)} \\
      &       &       &       &       &       &       &       &       &       &  \\
\midrule
Observations & \multicolumn{1}{l}{1285} & \multicolumn{1}{l}{1285} & 1285  & \multicolumn{1}{l}{1285} & 1285  & \multicolumn{1}{l}{1285} & 1285  & \multicolumn{1}{l}{1285} & \multicolumn{1}{l}{1285} & \multicolumn{1}{l}{1285} \\
Dummy subcourts & \multicolumn{1}{l}{NO} & \multicolumn{1}{l}{YES} & YES   & \multicolumn{1}{l}{YES} & YES   & \multicolumn{1}{l}{YES} & YES   & \multicolumn{1}{l}{YES} & \multicolumn{1}{l}{YES} & \multicolumn{1}{l}{YES} \\
Conditioning on notified & \multicolumn{1}{l}{YES} & \multicolumn{1}{l}{YES} & YES   & \multicolumn{1}{l}{YES} & YES   & \multicolumn{1}{l}{YES} & YES   & \multicolumn{1}{l}{YES} & \multicolumn{1}{l}{YES} & \multicolumn{1}{l}{YES} \\
R-squared & \multicolumn{1}{l}{0.00392} & \multicolumn{1}{l}{0.0449} & 0.0457 & \multicolumn{1}{l}{0.0905} & 0.0500 & \multicolumn{1}{l}{0.102} & 0.0494 & \multicolumn{1}{l}{0.448} & \multicolumn{1}{l}{0.343} & \multicolumn{1}{l}{0.222} \\
DepVarMean & \multicolumn{1}{l}{0.197} & \multicolumn{1}{l}{0.197} & 0.197 & \multicolumn{1}{l}{0.197} & 0.197 & \multicolumn{1}{l}{0.197} & 0.197 & \multicolumn{1}{l}{0.519} & \multicolumn{1}{l}{0.453} & \multicolumn{1}{l}{0.453} \\
\% Treated &       &       & 0.519 &       & 0.453 &       & 0.355 &       &       &  \\
\bottomrule
\bottomrule
\end{tabular}%

>>>>

% Table generated by Excel2LaTeX from sheet 'ITT_ATT'
\begin{tabular}{lrrlrlrlrrr}
      & \multicolumn{7}{c}{Conciliation}                      & \multicolumn{1}{c}{Calculator Plaintiff} & \multicolumn{1}{c}{Calculator Defendant} & \multicolumn{1}{c}{Calculator Both} \\
\cmidrule{2-11}      & \multicolumn{1}{c}{ITT} & \multicolumn{1}{c}{ITT} & \multicolumn{2}{c}{ATT (Plaintiff)} & \multicolumn{2}{c}{ATT  (Defendant)} & \multicolumn{1}{c}{ATT (Both)} & \multicolumn{3}{c}{First Stage} \\
\cmidrule{2-11}Treatment  & \multicolumn{1}{l}{0.0540*} & \multicolumn{1}{l}{0.0486**} &       &       &       &       &       & \multicolumn{1}{l}{0.234***} & \multicolumn{1}{l}{0.146***} & \multicolumn{1}{l}{0.489***} \\
      & \multicolumn{1}{l}{(0.0264)} & \multicolumn{1}{l}{(0.0202)} &       &       &       &       &       & \multicolumn{1}{l}{(0.0182)} & \multicolumn{1}{l}{(0.0117)} & \multicolumn{1}{l}{(0.0263)} \\
Calculator  & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & 0.208** &       & 0.333** &       & 0.0995** &       &       &  \\
(instrumented with ITT) & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & (0.0891) &       & (0.136) &       & (0.0417) &       &       &  \\
Calculator  &       &       &       & \multicolumn{1}{l}{-0.0364} &       & \multicolumn{1}{l}{-0.0388} &       &       &       &  \\
(instrumented with ITT \& ITT*EP) &       &       &       & \multicolumn{1}{l}{(0.0688)} &       & \multicolumn{1}{l}{(0.108)} &       &       &       &  \\
Constant  & \multicolumn{1}{l}{0.159***} & \multicolumn{1}{l}{0.124***} & 0.119*** & \multicolumn{1}{l}{0.127***} & 0.126*** & \multicolumn{1}{l}{0.0992***} & 0.125*** & \multicolumn{1}{l}{0.0234} & \multicolumn{1}{l}{-0.00657} & \multicolumn{1}{l}{-0.00841} \\
      & \multicolumn{1}{l}{(0.0184)} & \multicolumn{1}{l}{(0.0286)} & (0.0323) & \multicolumn{1}{l}{(0.0284)} & (0.0261) & \multicolumn{1}{l}{(0.0335)} & (0.0280) & \multicolumn{1}{l}{(0.0247)} & \multicolumn{1}{l}{(0.0217)} & \multicolumn{1}{l}{(0.0287)} \\
      &       &       &       &       &       &       &       &       &       &  \\
\midrule
Observations & \multicolumn{1}{l}{1285} & \multicolumn{1}{l}{1285} & 1285  & \multicolumn{1}{l}{1285} & 1285  & \multicolumn{1}{l}{1285} & 1285  & \multicolumn{1}{l}{1285} & \multicolumn{1}{l}{1285} & \multicolumn{1}{l}{1285} \\
Dummy subcourts & \multicolumn{1}{l}{NO} & \multicolumn{1}{l}{YES} & YES   & \multicolumn{1}{l}{YES} & YES   & \multicolumn{1}{l}{YES} & YES   & \multicolumn{1}{l}{YES} & \multicolumn{1}{l}{YES} & \multicolumn{1}{l}{YES} \\
Conditioning on notified & \multicolumn{1}{l}{YES} & \multicolumn{1}{l}{YES} & YES   & \multicolumn{1}{l}{YES} & YES   & \multicolumn{1}{l}{YES} & YES   & \multicolumn{1}{l}{YES} & \multicolumn{1}{l}{YES} & \multicolumn{1}{l}{YES} \\
R-squared & \multicolumn{1}{l}{0.00392} & \multicolumn{1}{l}{0.0449} & .     & \multicolumn{1}{l}{.} & .     & \multicolumn{1}{l}{.} & 0.0494 & \multicolumn{1}{l}{0.0900} & \multicolumn{1}{l}{0.0507} & \multicolumn{1}{l}{0.222} \\
DepVarMean & \multicolumn{1}{l}{0.197} & \multicolumn{1}{l}{0.197} & 0.197 & \multicolumn{1}{l}{0.197} & 0.197 & \multicolumn{1}{l}{0.197} & 0.197 & \multicolumn{1}{l}{0.519} & \multicolumn{1}{l}{0.453} & \multicolumn{1}{l}{0.453} \\
\% Treated &       &       & 0.519 &       & 0.453 &       & 0.355 &       &       &  \\
\bottomrule
\bottomrule
\end{tabular}%
